Earth_microbiome_MS

### 2019-07-11 Earth_microbiome_MS.Rmd
updated

---
title: "MRD_final_microbiome"
author: "Reis-Dehabadi, M"
date: "4/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~/globalmicrobiome')
# test
#test
#test
#clash 1
#clash2maryam

@@

```{r functions}

##### FUNCTIONS ########
##### Normalization #######

@@

## Data Set-up
```{r Data set-up}

#setwd("/Users/maryam/Scripts/Microbiome")

	## Get data
	library(foreign)
	library(stargazer)
	library(psych)
	library(plyr)
	library(xtable)
	library(car)
	#library(dplyr)
	library(scales)
	library(reshape) 
	library(gmodels)
	library(nnet)
	library(tidyr)
	library(sjmisc)
	library(RColorBrewer)
  library(htmltools)
	library(broom)

#The phyloseq package seeks to address issues with multiple microbiome analysis packages by providing a set of functions that internally manage the organizing, linking, storing, and analyzing of phylogenetic sequencing data. In general, this package is used for UniFrac analyses.
library(phyloseq)
library(microbiome)
library(knitr)
library(ggpubr)
#library(phylogeo)
library(dplyr)
#Graphing package used in phyloseq. To edit the default setting of a plot, you need to use functions in this package.
library(ggplot2)
library(viridis) 
library(cowplot)
# install.packages("devtools")
library(devtools)
# install_github("opisthokonta/tsnemicrobiota")
library(tsnemicrobiota)
# check you've installed this library
library(forcats)

# Data from http://dx.doi.org/10.1038/ncomms7342
#This data set contains genus-level microbiota profiling with HITChip for 1006 western adults with no reported health complications.

pseq <- baseline(atlas1006) # only uses the baseline samples. This is n=1006

>>>>

---
title: "Earth_microbiome_MS"
author: "Muriel Sirgi"
date: "03/07/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#setting the working directory in globalmicrobiome (GitHub directory)
knitr::opts_knit$set(root.dir = '~/globalmicrobiome')

@@

##Data Set-up
```{r R Library Set-up}

## Get data

#libraries for data processing and formatting
	library(foreign)
	library(stargazer)
	library(psych)
	library(plyr)
	library(xtable)
	library(car) #

	#library(dplyr)

	library(scales)
	library(reshape)
	library(gmodels) #
  library(nnet)
	library(tidyr) #works well with dplyr data pipelines

	library(sjmisc)
	library(RColorBrewer)
  library(htmltools) #
	library(broom)

#The phyloseq package seeks to address issues with multiple microbiome analysis packages by providing a set of functions that internally manage the organizing, linking, storing, and analyzing of phylogenetic sequencing data. In general, this package is used for UniFrac analyses.
library(phyloseq)
library(microbiome)
library(knitr)
library(ggpubr)
#library(phylogeo)
library(dplyr)
#Graphing package used in phyloseq. To edit the default setting of a plot, you need to use functions in this package.
library(ggplot2)
library(viridis) 
library(cowplot)
# install.packages("devtools")
library(devtools)
# install_github("opisthokonta/tsnemicrobiota")
library(tsnemicrobiota)
# check you've installed this library
library(forcats)
#package required for biomformat
library(jsonlite)
library(Matrix)
library(rhdf5)
#package used to work with biom files in R 
library(biomformat)

##Microbiome Data Import
```{r Microbiome Data Import}
#file.choose() has been chosen here to take away any errors pertaining to the file path while investigating the files from the ftp directory
githubdata_biom = file.choose()

#This function transforms a biom file into a phyloseq class object
githubdata_phyloseq = read_biom2phyloseq(githubdata_biom)

```{r Import GitHUb file (metada)}
read.table
```

```{r Microbiome Data Import Draft}
#import_biom("~/globalmicrobiome/emp_cr_silva_16S_123qc_filtered.biom") 
#import_biom(BIOMfilename = '~/globalmicrobiome/emp_cr_gg_13_8.release1.biom')
#biomfile <- file.choose("~/globalmicrobiome/emp_cr_gg_13_8.release1.biom")
#read_biom2phyloseq(biom.file = biomfile)
#import_biom('~/globalmicrobiome/emp_cr_gg_13_8.qc_filtered.biom')
#import_biom('~/globalmicrobiome/emp_cr_silva_16S_123.qc_filtered.biom'

#silva_closedref_biom <- system.file("extdata", "/Users/Muriel/globalmicrobiome/emp_cr_silva_16S_123qc_filtered.biom", package = "phyloseq")
#sample_metadata("/Users/Muriel/globalmicrobiome/emp_cr_silva_16S_123qc_filtered.biom")

#silva_closedref_biom = system.file("extdata", "~/globalmicrobiome/emp_cr_silva_16S_123qc_filtered.biom", package = "biomformat")

#silva_data = sample_metadata(silva_closedref_biom)

#biomfile = "/Users/Muriel/globalmicrobiome/emp_cr_silva_16S_123qc_filtered.biom"
#read_biom(biomfile)
#x = read_biom(biomfile)
#header(x)
#biom_shape(x)
#nrow(x)
#ncol(x)
#rownames(x)
#colnames(x)
#matrix_element_type(x)
#biom_data(x)

#Microbiome Functions (Nik)
```{r functions (Nik)}
##### FUNCTIONS ########
##### Normalization #######

@@

```{r }
